High-Dimensional Regularized Discriminant Analysis

### 2016-01-20 reports/paper-hdrda.Rnw
Figures and Tables moved to end. Placeholders in text.

@@

@@

@@

@@

>>>>

\[ \left[\text{Insert Figure \ref{fig:hdrda-contours} approximately here }\right] \]

@@

\[ \left[\text{Insert Figure \ref{fig:sim-results} approximately here }\right] \]

@@

\[ \left[\text{Insert Figure \ref{fig:sim-results-by-p} approximately here }\right] \]

@@

\[ \left[\text{Insert Table \ref{tab:microarray-results} approximately here }\right] \]

@@

\clearpage

\clearpage

\clearpage

\clearpage
